%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Senior Principal Technologist} % Job title
    {Singapore Airlines} % Organization
    {Singapore} % Location
    {Sep, 2023 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Strategic Mobile Architecture \& Optimization: Spearheaded the One Channel strategy (SAA/SQM), designing high-performance WebView architectures (JSBridge, precaching) and optimizing critical paths like Manage Booking to achieve competitive search and load times against industry benchmarks.}
        \item {GenAI-Driven SDLC Transformation: Revolutionized the development lifecycle by operationalizing Generative AI for automated user story generation, code assessment, and batch translations (using Claude Code/Jenkins), successfully reducing development cycle times and integrating AI-driven workflows into daily engineering practices.}
        \item {Technical Leadership \& Re-architecture: Led the strategic transition from outsourcing to in-house development (insourcing) for critical projects including ORCVS, MealVS, and ATVS, driving the adoption of Hexagonal Architecture and Domain-Driven Design (DDD), and standardizing Schema Libraries for core airline entities.}
        \item {Engineering Analytics \& Efficiency: Designed and deployed the SQLens engineering metrics dashboard using AWS QuickSight to visualize key performance indicators (Cycle Time, Release Frequency, Defect Escape Rate), cleaning complex JIRA datasets to establish data-driven transparency and drive team productivity improvements.}
        \item {Mentorship \& Team Development: Established comprehensive mentorship programs and technical guilds to foster a One Code Base culture, actively mentoring Tech Leads and Senior Engineers while collaborating with cross-functional stakeholders to align technical execution with business value (e.g., cost savings and microsite goals).}
      \end{cvitems}
    }


  \cventry
    {Vice President of Engineering} % Job title
    {Lazada South East Asia Pte Ltd, Alibaba Group} % Organization
    {Singapore} % Location
    {Mar, 2021 - Aug, 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and managed 11 commercial data products for internal \& external stakeholders with good user satisfaction.}
        \item {Consistently designed and enhanced the technical architecture to improve the product user experience, system stability, and developer efficiency.}
        \begin{itemize}
        		\item {Implemented entity change logging service based on Java serialization and use Java AOP to make it unintrusive on business logic.}
       	 	\item {Implemented staging and production data segregation solution using Mybatis plugin and Alibaba Druid.}
        		\item {Implemented database disaster recovery mechanism circuit breaking on master/backup database instances using sentinel library.}
		\item {Improved API response time performance using cache, parallel processing, and SQL optimization by up to 35 times.}
		\item {Developed using local test driven development, reusable software components, and low-code Function As a Service platform.}
	\end{itemize}
        \item {Successfully built a pipeline of ETL data processing and machine learning model execution with Alibaba SchedulerX platform, in order to automate the process of model execution and data synchronization jobs for Lazada \& Citibank Data Project and RedMart Price Kaki Project. It freed one developer from the mundane manual execution job so that he can spend more time on other projects.}
        \item {Monitored and reported on the system stability issues by using monitoring dashboard and linux application logs.}
        \item {Split large and complex requirements into product increments, organized sprint planning sessions \& standups, and assigned tasks to developers.}
        \item {Led a 12-person team including Frontend (7) and Backend (5) engineers in the regional data team, hired, coached, and developed talent.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Engineer, Software} % Job title
    {Singapore Press Holdings} % Organization
    {Singapore} % Location
    {Jul, 2019 - Mar, 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with product managers and stakeholders to adopt the new market trend features into the products.}
        \item {Built fully automated CI/CD pipelines on AWS for containerized applications using Docker, AWS ECR and CodeDeploy.}
        \item {Designed a Behavior-Driven Rewards and Loyalty API SaaS product using the microservices architecture.}
        \item {Implemented several API microservices in Node.js Express and the Admin Portal in React/Redux.}
        \item {Deployed a centralized logging environment(ELK, CloudWatch, S3) which gather log data from docker containers and AWS resources.}
        \item {Zaobao Rewards Loyalty Programme won the Best in Audience Engagement in ADMA 2020. Since released to the market in Feb 2020, the program has lifted the audience engagement by 59\%.}
        \item {Led a rewards and loyalty platform team (6 developers) and a digital sales and group marketing team (6 developers) using Scrum.}
        \item {Drove an interest group (Advanced Technology Lab) for AR/VR, AI, \& blockchain technology in the media industry.}
      \end{cvitems}
    }

%%---------------------------------------------------------
%  \cventry
%    {Principal Engineer, Software} % Job title
%    {Circles.Life} % Organization
%    {Singapore} % Location
%    {Dec, 2018 - Jun, 2019} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Built, architected and led the development of the telco BSS (business support system) middleware, which sped up the reliability and performance by 10 times.}
%        \item {Recruited principal engineers, engineering leads, and senior software engineers.}
%        \item {Mentored other developers, and led and shared DevOps best practice.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
  \cventry
    {Senior Developer} % Job title
    {Wirecard Asia Holding Pte. Ltd.} % Organization
    {Singapore} % Location
    {May, 2017 - Jun, 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a data cleansing and verification platform in Node.js Express and Angular.JS for parsing regional merchant documents.}
        \item {Built data pipelines to migrate the data into the more structured data models in Data Warehouse.}
        \item {Designed and built D3.js widget to visualize and customize the enterprise entity hierarchy.}
        \item {Developed an automated massive parallel processing pipeline to calculate merchant transaction fees, which resulted in 20 times processing speed and 2 times cost reduction.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisory Software Engineer} % Job title
    {IBM} % Organization
    {Singapore} % Location
    {Mar, 2013 - May, 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed enterprise applications for two blockchain projects, which got public exposure in MAS FinTech Festival 2016.}
        \item {Responsible for the UX/UI conceptual design, UI and backend API implementation, application’s continuous integration with cloud, and project management.
        }
        \item {Built an automated data ETL system, and developed a web app for real-time visualization of all the vessels and heat-map visualization of the congested areas in the Singapore port.
        }
        \item {Developed train simulation visualization module, passenger flow visualization in React based on origin-destination pair predictive analytics, and incident analytics module.}
        \item {Developed a solution on mobile platform for identifying dengue hotspots using the information collected by operators. Demonstrated the solution's capability to prevent dengue outbreaks.}
        \item {Developed a web search engine in React on Bluemix (PaaS) to make the local charity organizations more transparent and eventually help charity donors to donate more efficiently.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
